gender and age in food incentive

### 2024-02-20 outputs/paper/paper.qmd

# Create the bar graph
ggplot(public_no_incentives, aes(x = Stayed, y = prop, fill = Stayed)) +
  geom_col() +
    geom_text(aes(label = round(prop, 2)), 
            position = position_dodge(width = 0.9), 
            vjust = -0.5, # Adjust the vertical position of the labels
            color = "black",
            size = 3) +
  labs(x = "Choice",
       y = "Proportion") +
  scale_fill_manual(values = c("Changed" = '#BDBDBD', "Stayed Cookie" = '#757575', "Stayed Grape" = '#424242')) +
  ylim(0,0.5) +
  theme_minimal()
```

>>>>

# Create the bar graph
ggplot(public_no_incentives, aes(x = Stayed, y = prop, fill = Stayed)) +
  geom_col() +
    geom_text(aes(label = round(prop, 2)), 
            position = position_dodge(width = 0.9), 
            vjust = -0.5, # Adjust the vertical position of the labels
            color = "black",
            size = 3) +
  labs(x = "Choice",
       y = "Proportion") +
  scale_fill_manual(values = c("Changed" = '#BDBDBD', "Stayed Cookie" = '#757575', "Stayed Grape" = '#424242')) +
  ylim(0,0.6) +
  theme_minimal()
```
